---
title: "Court_Data"
output: html_document
date: "2023-06-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r load data}
library(tidyverse)
library(janitor)
library(lubridate)
fee <- read_csv("Input/website_merged.csv") %>% clean_names()
```

```{r counts}
table <- fee %>% count(region, court)
fee %>% count(law)
vtl <- fee %>% 
  filter(startsWith(law, "V"))

table <- vtl %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(county, court, arresting_agency) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

table %>% write_csv("Output/table.csv")
```

```{r}

byrace <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(race, county) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

byrace %>% write_csv("Output/byrace.csv")

```

```{r}
overall <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(county) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

overall %>% write_csv("Output/overall.csv")
```

```{r}
library(dplyr)

# Read the data frames
overall <- read.csv("Output/overall.csv")
revenue <- read.csv("Output/County_Revenue_21.csv")

# Join the data frames based on county name
joined_data <- left_join(overall, revenue, by = "county")


joined_data %>% write_csv("Output/overall.csv")

```

```{r}
court <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(court) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

byrace %>% write_csv("Output/court.csv")
```

```{r}

top_charge <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(top_charge_at_arraignment) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

top_charge %>% write_csv("Output/top_charge.csv")
```
```
```{r}
top_charge <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(top_charge_at_arraignment) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))
```{r}

```

top_charge %>% write_csv("Output/top_charge.csv")
```
```{r}
top_charge <- fee %>% 
  mutate_at(vars(contains("_imposed")), ~replace_na(.,0)) %>%
  group_by(top_charge_at_arraignment) %>%
  summarise(n_charges = n(),
            fines = sum(fines_imposed),
            fees = sum(fees_imposed),
            surcharges = sum(surcharges_imposed)) %>%
  mutate(total = fines + fees + surcharges) %>%
  mutate_if(is.numeric,~round(.,0))

top_charge %>% write_csv("Output/top_charge.csv")
```
